\plaintitle

### 2016-09-21 drafts/labor/piecework_lit.tex
compilation fix

\topic{Piecework may have started in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took off on in farm work \cite{hughRaynbirdTaskWork},
in textiles \cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads \cite{Brown01041990}, and 
elsewhere in manufacturing \cite{10.2307/3827491}.
Fordism and scientific management thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.}
\citeauthor{hart2013rise} point out that the Second World War,
which called millions of Americans to military service,
necessitated the rapid training and employment of
a labor pool that hadn't historically been utilized in industrial labor: women
\cite{hart2013rise}.
% With little time and virtually none of the training that was conventionally expected of metalworkers and other industrial work
% (e.g. years--long apprenticeships),
% tasks had to be redesigned and workers trained for these dramatically unorthodox task designs
\ali{I'd like to bring the Rosie the Riveter anecdote in here but it's not feeling natural\dots}
% \cite{honey1985creating,davies2014origins}.

>>>>

\topic{Piecework may have started in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took off on in farm work \cite{hughRaynbirdTaskWork},
in textiles \cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads \cite{Brown01041990}, and 
elsewhere in manufacturing \cite{10.2307/3827491}.
Fordism and scientific management thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.
\citeauthor{hart2013rise} point out that the Second World War,
which called millions of Americans to military service,
necessitated the rapid training and employment of
a labor pool that hadn't historically been utilized in industrial labor: women
\cite{hart2013rise}.
% With little time and virtually none of the training that was conventionally expected of metalworkers and other industrial work
% (e.g. years--long apprenticeships),
% tasks had to be redesigned and workers trained for these dramatically unorthodox task designs
\ali{I'd like to bring the Rosie the Riveter anecdote in here but it's not feeling natural\dots}
% \cite{honey1985creating,davies2014origins}.
